A Study on Penguins: A Minimal Reproducible Example

### 2024-08-23 01_Example/Manuscript.qmd
Add more comments

within(dat, {
  sex[is.na(sex)] <- "unknown"
  year <- as.factor(year) # Year is more interesting if analyzed as factor
}) |>
  (\(x) { # Add number of non-missings
    n <- sapply(x, \(v) sum(!is.na(v)))
    labels <- paste0(names(x), " (N=", n, ")")
    idx <- which(sapply(x, is.numeric))
    names(x) <- names(x) |>
      replace(
        list = idx,
        values = labels[idx]
      )
    x
  })() |>
  modelsummary::datasummary_balance(formula = ~ sex, output = "flextable", dinm = FALSE) |>
  flextable::theme_apa() |>
  flextable::font(fontname = "TeX Gyre Termes", part = "all")

>>>>

within(dat, {
  sex[is.na(sex)] <- "unknown"
  year <- as.factor(year) # Year is more interesting if analyzed as factor
}) |>
  (\(x) { # Add number of non-missings to labels
    n <- sapply(x, \(v) sum(!is.na(v))) # Calculate number of non-missings
    labels <- paste0(names(x), " (N=", n, ")") # Paste labels and numbers together
    idx <- which(sapply(x, is.numeric)) # Get numeric variables
    names(x)[idx] <- labels[idx] # Change the labels
    x
  })() |>
  modelsummary::datasummary_balance(formula = ~ sex, output = "flextable", dinm = FALSE) |>
  flextable::theme_apa() |>
  flextable::font(fontname = "TeX Gyre Termes", part = "all")
